\newpage
\section{Mutations}

\subsection{Mutations Overview}

\begin{enumerate}\itemsep0pt
    \item \textbf{Add Neuron} \\
    Add a neuron to an existing cluster. The neuron will be placed on an existing connection.  
    A $\rightarrow$ B becomes A $\rightarrow$ C $\rightarrow$ B, where A and B are existing neurons and C is the newly placed neuron.
    
    \item \textbf{Add Connection} \\
    Add a new connection between a pair of neurons on an existing cluster.
    
    \item \textbf{Disable Connection} \\    
    Mark an existing connection as disabled.
    
    \item \textbf{Nudge Weight} \\    
    Nudge the weight of an existing connection by a small delta value.
    
    \item \textbf{Change Placement Neuron} \\    
    Change the neuron that is marked as the placement neuron on a cluster.
    
    \item \textbf{Add New Cluster} \\    
    Add a new cluster and place it through a new hox gene.
    
    \item \textbf{Copy Cluster} \\    
    Create a copy of an existing cluster and place it through a new hox gene.
    
    \item \textbf{Desync Cluster} \\    
    Allow a cluster to mutate independently by turning it into a new cluster.
    
    \item \textbf{Bridge} \\    
    Add a new cluster in between two clusters that share a neuron.
    
    \item \textbf{Add Hox With Existing Cluster} \\    
    Add a new hox gene that places an existing cluster.
    
    \item \textbf{Change Target Neuron} \\    
    Change the target neuron of a hox gene.
    
    \item \textbf{Duplicate Hox} \\    
    Add a new hox gene to the end of the genome with the same configuration as an already existing one.
    
\end{enumerate}
